---
title: 'R package beginr released on CRAN'
author: "赵鹏"
date: '2017-06-23'
slug: beginr-released
summary: "beginr is a collection of useful functions for R beginners. It might be helpful to R experts as well."
tags:
  - R
  - beginr
  - post
banner: img/banners/logo-beginr.png
bibliography: ["zhaor.bib"]
categories: []
output: #md_document
  md_document:
    variant: markdown_github
---

I’m glad to announce that 'beginr' [@R-beginr] is now on [CRAN](https://CRAN.R-project.org/package=beginr). This post is a brief documentation of 'beginr 0.1.0'. Subsequent updates can be found on the [GitHub site of beginr](http://github.com/pzhaonet/beginr).

<!--more-->

![](http://cranlogs.r-pkg.org/badges/grand-total/beginr)


# Introduction 

'beginr' is a collection of useful functions for R beginners, including hints for the arguments of the 'plot()' function, self-defined functions for error bars, user-customized pair plots and hist plots, enhanced linear regression figures, etc.. This package could be helpful to R experts as well.

# Installation

```{r, eval=FALSE}
# stable version on CRAN
install.package("beginr")
# or development version on GitHub
devtools::install_github("pzhaonet/beginr")
```

# Quick Start

## Functions as Memos

If you often forget the options for `pch`, `lty`, `type`, and `col` when you `plot()`, you can run `plotpch()`, `plotlty()`, `plottype()`, `plotcolors()`, and `plotcolorbar()`. No need to search the internet any more.

```{r}
beginr::plotpch()
beginr::plotlty()
beginr::plottype()
beginr::plotcolors()
beginr::plotcolorbar()
```

## Functions for Easy Plotting

Linear regression is often used in scientific work, but it is annoying to display the results. In R you have to run `lm()`, `plot()`, `abline()`, `text()` and so on and so forth. Now with 'beginr' you only have to run `plotlm()`.

```{r}
x <- 1:10
y <- 1:10 + rnorm(10)
beginr::plotlm(x, y)
```

If you want to display the distribution of a data-set, use `plothist()`, which gives you a histogram with markers of the median, mean, quantiles, standard deviation, sample number and the skewness.

```{r}
x <- rnorm(10000)
beginr::plothist(x)
```

I like `pairs()`, and 'beginr' gives more powerful features to `plotpairs()` and `plotpairs2()`.

```{r}
df <- data.frame(a = 1:10, b = 1:10 + rnorm(10), c = 1:10 + rnorm(10))
beginr::plotpairs(df)
beginr::plotpairs2(df)
```

I often have to plot one independent variable (x) and multiple dependent variables  (y~1~, y~2~, ..., y~n~) in one 2-D coordinate system, or one dependent variable (y) against multiple independent variables (x~1~, x~2~, ..., x~n~) with their error bars. Use `dfplot()` or `dfplot2()` in 'beginr'.

```{r}
x <- seq(0, 2 * pi, length.out = 100)
y <- data.frame(sin(x), cos(x))
yerror <- data.frame(abs(rnorm(100, sd = 0.3)), abs(rnorm(100, sd = 0.1)))
beginr::dfplot(x, y, yerror = yerror)
beginr::dfplot2(y, x, xerror = yerror)
```

If you would like to add errorbars only, then use `errorbar()`.

```{r}
x <- seq(0, 2 * pi, length.out = 100)
y <- sin(x)
plot(x, y, type = "l")
beginr::errorbar(x, y, yupper = 0.1, ylower = 0.1)
```

## Functions for Data Frames

`lmdf()` performs the linear regression between every two columns in a data frame.

```{r}
df <- data.frame(a = 1:10, b = 1:10 + rnorm(10), c = 1:10 + rnorm(10))
beginr::lmdf(df)
```

There are two functions as improvements of `tapply()` for factor calculation.

```{r, eval=FALSE}
beginr::tapplydf()
beginr::tapplydfv()
```

## Functions for Reading and Writing files

`readdir()` reads multiple files into a list.

```{r, eval=FALSE}
beginr::readdir()
```

`writefile()` avoids overwriting the files which already exist.

```{r, eval=FALSE}
beginr::writefile()
```

`list2ascii()` saves a list as a text file.

```{r, eval=FALSE}
alist <- list(a = 1:10, b = letters)
beginr::list2ascii(alist)
```

## Functions for Packages

`bib()` creates bibliographic entries as texts or a file ('.bib').

```{r, warning=FALSE}
beginr::bib(pkg = c("mindr", "bookdownplus", "pinyin", "beginr"))
```

`plotpkg()` displays a figure showing the downloads of packages.

```{r, fig.asp=0.3}
beginr::plotpkg("beginr", from = "2017-06-23")
```

`rpkg()` creates a new R package in an easy way.

```{r, eval=FALSE}
beginr::rpkg()
```


# References
